FraCaS: 80 percent complete

### 2019-01-18 paper2018/paper.tex
typography
sec. 3

\usepackage[backend=bibtex,citestyle=authoryear,style=alphabetic,natbib]{biblatex}
\addbibresource{PaperTools/bibtex/jp.bib}
\addbibresource{phorae.bib}

@@

\paragraph{Adverbs}
Another point, of minor theoretical importance but major practical
one, is our handling of adverbial phrases. We interpret adverbs (and
in general all adverbial and prepositional phrases) are VP-modifiers:
$Adv = VP -> VP$, where $VP = object -> Prop$. However, applying
adverbs to verb-phrases heavily complicates the Coq proofs, because
such phrases can contain quantifiers. Therefore, we instead move the
adverbs, so that they apply to (atomic) verbs only, and can simplify
proofs accordingly. \todo{theoretical justification in the literature}

\section{Results and evaluation}
% - show overall numbers
% - compare with others
% - error analysis (classify, show examples)

>>>>

\usepackage[backend=bibtex,citestyle=authoryear,style=alphabetic,natbib]{biblatex}
\addbibresource{PaperTools/bibtex/jp.bib}
\addbibresource{phorae.bib}
\addbibresource{IWCSbib.bib}

\usepackage{stmaryrd}
\usepackage{newunicodechar}
\input{PaperTools/latex/newunicodedefs}

@@

\paragraph{Adverbs}
Another point, of minor theoretical importance but major practical
one, is our handling of adverbial phrases. We interpret adverbs (and
in general all adverbial and prepositional phrases) are VP-modifiers:
$Adv = VP → VP$, where $VP = object → Prop$. However, applying
adverbs to verb-phrases heavily complicates the Coq proofs, because
such phrases can contain quantifiers. Therefore, we instead move the
adverbs, so that they apply to (atomic) verbs only, and can simplify
proofs accordingly. \todo{theoretical justification in the literature}

\section{Results and evaluation}

We evaluated FraCoq against 8 sections of the FraCaS test suite, for a
total of 259 examples. We excluded only one section, 7. The reason for
doing so is that, in our view, it contains too many examples which
require \textit{ad-hoc} treatment, and thus makes little sense to
include without complementing it with a more thorough suite which
captures a more complete landscape of the phenomena that section 7
touches.

We classify as YES if a proof can be constructed from the premises to
the hypothesis, NO if a proof of the negated hypothesis can be
constructed and UNK otherwise.\footnote{Because we work with a non-decidable logic, that poses a theoretical question that we address below.}

%  ------ Section 1
% complete: 74/74   []
% correct: 71/74   [13,14,46]
% score: 0.9594594594594594
%  ------ Section 2
% complete: 33/33   []
% correct: 27/33   [84,91,94,95,109,111]
% score: 0.8181818181818182
%  ------ Section 3
% complete: 27/28   [137]
% correct: 24/27   [124,126,127]
% score: 0.8571428571428571
%  ------ Section 4
% complete: 47/52   [171,172,191,193,195]
% correct: 45/47   [170,188]
% score: 0.8653846153846154
%  ------ Section 5
% complete: 20/20   []
% correct: 19/20   [216]
% score: 0.95
%  ------ Section 6
% complete: 29/31   [244,245]
% correct: 27/29   [242,250]
% score: 0.8709677419354839
%  ------ Section 7
% complete: 0/67   [251,252,253,254,255,258,259,260,261,262,263,264,265,266,267,268,269,270,271,272,273,274,275,277,278,279,280,281,282,283,284,285,286,287,288,289,290,292,293,294,295,296,297,298,299,300,301,302,303,304,306,307,311,312,313,314,315,316,317,318,319,320,321,322,323,324,325]
% correct: 0/0   []
% score: 0.0
%  ------ Section 8
% complete: 8/8   []
% correct: 6/8   [326,333]
% score: 0.75
%  ------ Section 9
% complete: 13/13   []
% correct: 12/13   [346]
% score: 0.9230769230769231
%  ------ Section 0
% complete: 251/259   [137,171,172,191,193,195,244,245]
% correct: 231/251   [13,14,46,84,91,94,95,109,111,124,126,127,170,188,216,242,250,326,333,346]
% score: 0.8918918918918919

\todo{rejected and changed cases in FraCaS}
\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & \# examples & Ours      & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74)  & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82       & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86       &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87       &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20)  & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87       & .56    & .48  & .45  &  -       \\
8 & Verbs        & 8           & .75       &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92       & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 262         & .89 (259) & .83    & .69  & .50  & .85 (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of examples shown in the
    third column, the actual number of examples attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}.  }
\end{table}

The above result reveals a considerable improvement over earlier
approaches in terms of coverage, with three more sections covered over
previous state of the art. Additionally, our system is generally best
in terms of accuracy overall. In particular, section 6 sees a large
improvement in accuracy, which we attribute to our new analysis of
comparatives, enabled by our dynamic semantics.

\todo{error analysis}
